---
title: "Kiva Loans"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Preprocessing data set
```{r}
#dat <- read.csv("/cloud/project/kiva_loans.csv")
#dat_mpi <- read.csv("/cloud/project/kiva_mpi_region_locations.csv")

#dat_merged <- merge(dat,dat_mpi,by=c("country","region"))
#final_dat <- dat_merged[order(dat_merged$MPI),]

```

## Reading the data set
```{r}
dat <- read.csv("kiva_loan.csv")
str(dat)
summary(dat)
```

## Exploring the data set
Come up with some basic plots:
barplots,
scatterplots,
histograms,
boxplots...
```{r}

```

## Fitting the model
Come up with some basic questions on what we need to predict...

Some ideas:

Predict the MPI:

The Global Multidimensional Poverty Index (MPI) was developed in 2010 by the Oxford Poverty & Human Development Initiative (OPHI) and the United Nations Development Programme. and uses different factors to determine poverty beyond income-based lists. It replaced the previous Human Poverty Index.

Predict the amount to be loaned:

Predict what they are using the money for:

```{r}


```

